---
title: "DVIEst user guide"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DVIEst user guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DVIEst)
```

<br>
Load sample files.
```{r}
climate <- read.table(system.file("extdata/climate.txt",
                                  package = "DVIEst"), header = TRUE)
dates <- read.table(system.file("extdata/dates.txt",
                                  package = "DVIEst"), header = TRUE)
```

<br>
Create a GaParam object to specify parameters for a genetic algorithm to 
estimate parameters of a DVI model.
```{r}
ga_param <- gaParam(maxiter = 100, parallel = 1)
```
<br>

Create a DviParam object to specify fixed parameters of a DVI model.
```{r}
fixed_param <- dviFixedParam()
```

<br>
Create a DviModel object as input for estDVIparam().
```{r}
dvi_model <- buildDVImodel(date = climate$Date, 
                           day_len = climate$DayLength,
                           temp = climate$Temp, 
                           sowing = dates$Sowing[dates$Name == "NKTP"],
                           heading = dates$Heading[dates$Name == "NKTP"], 
                           critical = 12.75000,
                           acc = "NKTP")
```

<br>
You can briefly check the summary of the DviModel object.
```{r}
summary(dvi_model)
```


<br>
Estimate parameters of a DVI model using a genetic algorithm.
```{r eval = FALSE}
# Do not run this code!
# The parameter estimation using a genetic algorithm is a computational burden.
dvi_est <- estDVIparam(object = dvi_model, 
                       fixed_param = fixed_param, 
                       ga_param = ga_param)
```
<br>
For a demonstration, set arbitrary values as estimated parameters of the DVI 
model.
```{r}
dvi_est <- setDviParam(object = dvi_model,
                       fixed_param = fixed_param,
                       alpha = 5.497095, 
                       beta = 7.1155689, 
                       g = 86.4446010)
```


<br>
Predict the heading date and days-to-heading based on the DVI model with the 
estimated parameters.
```{r}
dvi_est <- predict(dvi_est)
```

<br>
You can briefly check the summary of the DviEst object.
```{r}
summary(dvi_est)
```


<br>
Plot the observed and predicted days-to-heading. 
```{r fig.width=5, fig.height=5}
p <- plotDviEst(object = dvi_est)
print(p)
```

<br>
Extract the estimated parameters from the DviEst object.
```{r}
est_param <- getEstParam(object = dvi_est)
est_param
```

<br>
Extract the prediction from the DviEst object.
```{r}
pred_df <- getPred(object = dvi_est)
head(pred_df)
```
Predicted heading dates, observed days-to-heading, and predicted days-to-heading
from the left column to the right.

<br>
Extract the correlation coefficient from the DviEst object.
```{r}
cor_coef <- getCor(object = dvi_est)
cor_coef
```


<br>
<br>
Session Info.
```{r}
sessionInfo()
```

